\huge Tor's Usability for Censorship Circumvention

### 2016-05-12 lindas-ms-paper/lindas-ms-paper.tex
make a copy for my master's thesis.

\begin{figure}
  \centering
    \includegraphics[width=0.5\textwidth]{bridge-options.png}
%\small
%\begin{itemize}
%\renewcommand{\labelitemi}{$\circ$}
%\item Connect with provided bridges\\
%Transport type:
%\begin{itemize}
%\item flashproxy
%\item fte
%\item fte-ipv6
%\item meek-amazon
%\item meek-azure
%\item meek-google
%\item obfs3 (recommended)
%\item obfs4
%\item scramblesuit
%\end{itemize}
%\item Enter custom bridges\qquad\fbox{Help}\\
%\end{itemize}
\caption{
Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
Users are not familiar with the options under ``Transport type'' denote various
built-in circumvention technologies (``pluggable transports'').
Under ``Enter custom bridges,'' there is a space to paste in
a bridge line, obtained out of band.
The ``Help'' button displays instructions on obtaining
bridge lines. 
}
\label{fig:bridge-options}
\end{figure}

>>>>

\begin{figure}
  \centering
    \includegraphics[width=0.5\textwidth]{bridge-options.png}
%\small
%\begin{itemize}
%\renewcommand{\labelitemi}{$\circ$}
%\item Connect with provided bridges\\
%Transport type:
%\begin{itemize}
%\item flashproxy
%\item fte
%\item fte-ipv6
%\item meek-amazon
%\item meek-azure
%\item meek-google
%\item obfs3 (recommended)
%\item obfs4
%\item scramblesuit
%\end{itemize}
%\item Enter custom bridges\qquad\fbox{Help}\\
%\end{itemize}
\caption{
Bridge selection options in Tor Launcher for Tor Browser~5.0.3.
Users are not familiar with the options under ``Transport type,'' which are various
built-in circumvention technologies (``pluggable transports'').
Under ``Enter custom bridges,'' there is a space to paste in
a bridge line, obtained out of band.
The ``Help'' button displays instructions on obtaining
bridge lines. 
}
\label{fig:bridge-options}
\end{figure}
